Enhancing Adversarial Robustness for Deep Metric Learning

### 2021-11-04 robdml.tex
para

Then, how hard should such ``\emph{destination} hardness'' be?
%
Recall that the model is already prone to collapse with excessively hard benign
triplets~\cite{facenet}, let alone adversarial examples.
%
Thus, intuitively, the \emph{destination} hardness can be that of another
benign triplet which is harder than the given triplet (\eg, a
Semihard~\cite{facenet} triplet).
%
However, in the late phase of training, the
expectation of \emph{destination} hardness of another benign triplet
will be small, and close to the \emph{hardness} expectation of the given triplet.
%
This leads to weak attacks, and inefficient learning from a weak adversary.
%
Besides, we speculate a strong adversary in the early phase of DML training may
hinder the model from learning good embeddings, and hence influence the
eventual performance on benign examples.
%
Based on these, a \emph{destination} hardness calculated from benign examples
may not be the best choice.
%
A better \emph{destination} hardness should be able to balance the training
objectives in the early and late phases of training.

>>>>

Then, how hard should such ``\emph{destination} hardness'' be?
%
Recall that the model is already prone to collapse with excessively hard benign
triplets~\cite{facenet}, let alone adversarial examples.
%
Thus, intuitively, the \emph{destination} hardness can be the hardness of
another benign triplet which is moderately harder than the given triplet (\eg,
a Semihard~\cite{facenet} triplet).
%
However, in the late phase of training, the expectation of the difference
between such \emph{destination} hardness and that of the given triplet will be
small, leading to weak adversarial examples and inefficient adversarial
learning.
%
Besides, strong adversarial examples in the early phase of training may also
hinder the model from learning good embeddings, and hence influence the
performance on benign examples.
%
Namely, a better \emph{destination} hardness should be able to balance the
training objectives in the early and late phases of training.
